\documentclass{resume}

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{George P. de Souza Filho}
\address{+55 (61) 9 81835536 - PB}
\address{george7paulino@gmail.com}

\begin{document}

\textbf{Languages}: Native Portuguese, Intermediate English.

\textbf{Github}: \href{https://github.com/GeorgePaulino}{GeorgePaulino} \ 
\textbf{Linkedin}:  \href{https://www.linkedin.com/in/georgepaulino/}{in/georgepaulino}

%----------------------------------------------------------------------------------------
%	EXPERIÊNCIA
%----------------------------------------------------------------------------------------


\begin{rSection}{Experience}
    \item \textbf{\href{https://www.cogumeluns.com/}{Co-Founder – Cogumeluns Group}} \hfill 02/2025 – Present \\
    Co-founded an early-stage startup focused on innovation and creativity, developing services for both the general public and businesses.

    \item \textbf{\href{https://www.bb.com.br/site/}{Information Technology Advisor III - Banco do Brasil}} \hfill 09/2023 - Present \\
    Design, develop, and maintain enterprise banking systems leveraging Cloud and Mainframe technologies. Responsibilities include enhancing existing features, implementing new functionalities, and ensuring high availability, scalability, and security in compliance with banking standards and regulations.
\end{rSection} 

%----------------------------------------------------------------------------------------
%	EDUCAÇÃO
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    \item \textbf{\href{https://www.unibf.com.br/}{Bachelor’s Degree in Information Systems – UniBF Centro Universitário}} \hfill {07/2024 –  \emph{Expected: Dec 2026}} \\
    Coursework includes software engineering, database systems, cloud computing, and artificial intelligence.

    \item \textbf{\href{https://www.ifpb.edu.br/}{Technical Diploma in Multimedia – Instituto Federal da Paraíba}} \hfill {Feb 2019 – Dec 2021} \\
    Focused on digital design, web development, and multimedia production, integrating creative and technical skills.
\end{rSection}


%----------------------------------------------------------------------------------------
% SKILLS	
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\item \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Artificial Intelligence & PyTorch, Transformers, Pandas, Dataset Preparation \\
Cloud \& DevOps & Docker, VPS Deployment and Management \\
Databases & SQLite, SQL Server, Oracle DB \\
Server Technologies & WebLogic Server, VPS Configuration \\
Mainframe & IBM z16 \\
Mobile Development & React Native \\
Web Development & Next.js, Node.js \\
Tools & Git, Jenkins \\
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR
%----------------------------------------------------------------------------------------
\begin{rSection}{Extracurricular} \itemsep -1pt {}
    \item \textbf{\href{https://www.instagram.com/tailufpb/}{Member – TAIL (Technology and Artificial Intelligence League)}} \hfill 09/2022 – Present \\
    Collaborate on AI-focused projects, applying machine learning and data analysis techniques to solve real-world problems. Contribute to knowledge sharing and skill development among league members at UFPB.
    \item \textbf{\href{https://www.escolainvictus.com/}{Robotics Assistant – Invictus Colégio e Curso}} \hfill 02/2022 – 08/2022 \\
    Assisted in teaching programming and robotics to students, providing technical guidance and mentorship. Supported curriculum delivery and hands-on learning activities, leveraging practical expertise in coding and AI.
\end{rSection}


%----------------------------------------------------------------------------------------
%	PROJETOS
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\item \textbf{\href{https://enetrix.ufpb.br/}{Enetrix - UFPB - Website}} \hfill 06/2022 - 12/2022 \\
A project of interest to the United Nations regarding international and national energy security agreements. Developed by UFPB, the project was featured on the \href{https://www.un.org/en/academic-impact/insights-energy-diplomacy-and-un-data-intensive-research-brazilian-universities}{United Nations} portal. I was responsible for referencing articles and developing the official website.

\item \textbf{\href{https://github.com/ralfferreira/generate-abstract}{IAbstract – TAIL (AI Project)}} \hfill 06/2022 – 12/2022 \\
Developed a Natural Language Processing (NLP) system capable of automatically summarizing academic articles. Contributed to model training, evaluation, and metric development, improving the accuracy and efficiency of the summarization process. Project executed as part of TAIL during the first semester of college.

%\item \textbf{\href{https://georgepaulino.github.io/TicTacToe/}{Tic Tac Toe - Independent - Website}} \hfill 01/2022 \\
%A website to play Tic Tac Toe developed using React JavaScript with TypeScript. I independently worked on this project to study React and its technologies.

\end{rSection}

%----------------------------------------------------------------------------------------
%	CONQUISTAS
%----------------------------------------------------------------------------------------

\begin{rSection}{Achievements}

\item \textbf{\href{http://www.obmep.org.br/}{Multimedalist – Brazilian Mathematics Olympiad (OBMEP)}} \hfill 2015 – 2021 \\
Awarded two Bronze medals (2015, 2021) and one Silver medal (2018) in OBMEP, a nationally recognized and highly competitive mathematics competition in Brazil.

\item \textbf{\href{http://www.mat.ufpb.br/opm/}{Multimedalist – Olympiad of Mathematics of João Pessoa (OPM)}} \hfill 2018 – 2019 \\
Earned a Bronze medal (2018) and a Silver medal (2019) in OPM, a regional mathematics competition in Paraíba, demonstrating strong problem-solving skills and mathematical proficiency.

\end{rSection}

\end{document}
